Active Learning for SAT Solver Benchmarking {\large (extended and revised version)}

### 2024-05-28 paper_jar/paper.tex
Minor changes

The information-gain sampling strategy selects the instance with the highest expected entropy reduction regarding the runtime labels.
To be more precise, we select the instance $e \in \mathcal{I} \setminus \tilde{\mathcal{I}}$ that maximizes $IG(e)$, which is specified in the following equation:
%
\begin{equation*}
  \operatorname{IG}(e) := \operatorname{H}(e) - \sum_{n = 1}^{k} f_{\hat{a}}'(e)_{n} \operatorname{\hat H}(e)_n
\end{equation*}
%
In the equation, $\operatorname{H}(e)$ denotes the entropy of the runtime labels $\gamma(a, e)$ over all $a \in \mathcal{A}$ and $\operatorname{\hat H}(e)$ denotes the entropy of these labels plus the runtime label for $\hat{a}$.
The term $\operatorname{\hat H}(e)_n$ is computed for every possible runtime label $n \in \{1, \dots, k\}$.
By maximizing the information gain, instances are selected that identify solvers with similar runtime cluster labels, i.e., the new solver ranks similarly to the solvers in the same clusters.

>>>>

The information-gain sampling strategy selects the instance with the highest expected entropy reduction regarding the runtime labels.
To be more precise, we select the instance $e \in \mathcal{I} \setminus \tilde{\mathcal{I}}$ that maximizes $IG(e)$, which is specified in the following equation:
%
\begin{equation*}
  \operatorname{IG}(e) := \operatorname{H}(e) - \sum_{n = 1}^{k} f_{\hat{a}}'(e)_{n} \operatorname{\hat H}(e)_n
\end{equation*}
%
In the equation, $\operatorname{H}(e)$ denotes the entropy of the runtime labels $\gamma(a, e)$ over all $a \in \mathcal{A}$ and $\operatorname{\hat H}(e)$ denotes the entropy of these labels plus the runtime label for $\hat{a}$.
The term $\operatorname{\hat H}(e)_n$ is computed for every possible runtime label $n \in \{1, \dots, k\}$.
By maximizing the information gain, one favors instances whose most likely cluster labels, as determined by $f_{\hat a}'$, are similar to a great number of existing solvers.
This decreases the entropy among the cluster labels of the given instance and we know that the new solver performs similarly to a number of solvers.
